\section{Selected Projects}
% \bigskip
% \begin{adjustbox}{max width=\textwidth}
\begin{supertabular}{r|p{17.5cm}}

\emph{} & \normalsize \bf BLADE: Better Language Answers through Dialogue and Explanations (2025) \textsc{}  \\\textsc{}&\small{Conducted research study on the impact of using a knowledge-grounded conversational assistant on student performance in an undergraduate-level course.}\\&\footnotesize{Stack: RAG-based conversation assitant, Python}\\\multicolumn{2}{c}{} \vspace{-0.08in}\\ 
\emph{} & \normalsize \bf LLMs as Commonsense Knowledge generators for Natural Language Inference (NLI) (2025) \textsc{}  \\\textsc{}&\small{Evaluated LLMs as commonsense knowledge sources by generating axioms for NLI predictions on SNLI and ANLI datasets. Implemented an LLM-as-judge framework to scale evaluation and assess axiom factuality. 
% and consistency.
}\\&\footnotesize{Stack: Llama-3.1-70B-Instruct, Clause-3.5-Sonnet, Python}\\\multicolumn{2}{c}{} \vspace{-0.08in}\\


\emph{} & \normalsize \bf Fact Verification via AMR with Explainability (2024) \textsc{}  \\\textsc{}&\small{Developed an explainable fact verification pipeline using AMR graphs to assess meaning containment between claim and evidence. Combined AMR evaluation metrics with cosine similarity and provided post-hoc graph alignments for prediction interpretability.}\\&\footnotesize{Stack: Python, IBM transitioned-based AMR parser, Smatch, \(S^2\)match, SentenceBERT}\\\multicolumn{2}{c}{} \vspace{-0.08in}\\

\emph{} & \normalsize \bf Targeted Sentiment Analysis through Convolutional Networks (2023) \textsc{}  \\\textsc{}&\small{Developed a GCN-based entity recognition system combining dependency parsing, rule-based features, and token embeddings for node classification. Integrated the model into a targeted sentiment analysis pipeline and evaluated on SemEval 2014 ABSA dataset.}\\&\footnotesize{Stack: Python, SpaCy,  Dependency trees, Graph Convolutional Networks, DistilBERT}\\\multicolumn{2}{c}{} \vspace{-0.08in}\\

 \emph{} & \normalsize \bf Automatic Error Visualizing and Analyzing Tool (2021) \textsc{}  \\\textsc{}&\small{Developed a tool for the classification, visualization, and frequency analysis of translation errors in Sinhala-English Machine Translation systems. The tool identifies frequent translation errors to enhance system performance.}\\&\footnotesize{Stack : Python, NLTK, Jupyter Notebook.}\\\multicolumn{2}{c}{} \vspace{-0.08in}\\
 \emph{} & \normalsize \bf Improving Sinhala - English Machine Translation quality using Automatic Post Editing (APE) Techniques (2020)\textsc{}  \\\textsc{}&\small{Research  on current APE techniques and implementation of a suitable APE system to improve Sinhala - English Machine Translation quality}\\&\footnotesize{Stack : OpenNMT-py, OpenNMT-tf, Pytorch, LSTM, Transformer-Based Models.}\\\multicolumn{2}{c}{} \vspace{-0.08in}\\
 
 % \emph{} & \normalsize \bf Traffic light control system with Reinforcement learning   2019-2020 \textsc{}  \\\textsc{}&\small{Implementing a reinforcement learning agent to return adaptive traffic light time settings according to the existing traffic level.}\\&\footnotesize{Stack : Python, Tensorflow, SUMO traffic simulator, Q-Learning.}\\\multicolumn{2}{c}{} \\

 \textsc{} & \normalsize \bf Customer recommender solution for banking domain (2018) \\&\small {A customer recommender solution with a useful feature that enables the bank to describe customer behaviors and generate insight through them was designed and implemented using the customer transaction and demographic data available in a given bank database. }\\&\footnotesize{Stack : Python, PySpark, XGBoost, AWS virtual servers.}\\\multicolumn{2}{c}{} \\
 
% \textsc{} & \normalsize \bf Prediction model for customer check-ins for Hotel management 2018 \\&\small {Implementing a prediction model to predict the number of possible customer check-ins for a given day was designed and implemented to be used as a tool in hotel management processes.}\\&\footnotesize{Stack : Python, Microsoft Azure, XGBoost.}\\\multicolumn{2}{c}{} \\
  
\end{supertabular}