\section{Publications}
% % \bigskip
% \begin{itemize}
% \setlength\itemsep{0.01em}
%   \item \underline{Chathuri Jayaweera} and Bonnie Dorr. BLADE: Better Language Answers through Dialogue and Explanations. Preprint 2026
%   \item \underline{Chathuri Jayaweera}, Brianna Yanqui, Bonnie Dorr. Filling the Gap: Is Commonsense Knowledge Generation useful for Natural Language Inference?. Annual Meeting of the Association for Computational Linguistics (ACL). Under-review. arXiv: 2507.15100, 2026
%   \item \underline{Chathuri Jayaweera}, Bonnie Dorr. From Disagreement to Understanding: The Case for Ambiguity Detection
% in NLI. Accepted at NLPerspectives EMNLP 2025
%   \item \underline{Chathuri Jayaweera}, Sangpil Youm, and Bonnie Dorr. AMREx: AMR for Explainable Fact Verification. In Proceedings of the Seventh Fact Extraction and VERification Workshop (FEVER), pages 234–244, Association for Computational Linguistics, 2024
%   \item Sangpil Youm, Brodie Mather, \underline{Chathuri Jayaweera}, Juliana Prada and Bonnie Dorr. DAHRS: Divergence-Aware Hallucination Remediated SRL Projection. In International Conference on Applications of Natural Language to Information Systems, pages 423-438, Springer, 2024.
%   \item Manuel Nunez Martinez, Sonja Schmer-Galunder, Zoey Liu, Sangpil Youm, \underline{Chathuri Jayaweera}, and Bonnie J. Dorr. Balancing Transparency and Accuracy: A Comparative Analysis of Rule-Based and Deep Learning Models in Political Bias Classification. In Proceedings of the Second Workshop on Social Influence in Conversations (SICon 2024), pages 102–115, Association for Computational Linguistics, 2024.
%   \item \underline{Chathuri Jayaweera} and Gihan Dias. Automatic Classification, Visualization and Analysis of Errors in Machine Translation. In Extended Abstracts of International Conference on Information and Automation for Sustainability (ICIAFS), pages 43-44. IEEE, 2021.
%   \item Sutharsan, Mahendren, Shehan Rajakaruna, S. Y. Jayaweera, \underline{J. A. C. M. Jayaweera}, and Subramaniam Thayaparan. Vision-Based Adaptive Traffic Light Controller for Single Intersection.In proceedings of the International Conference on Information Technology Research (ICITR), pages. 1-6. IEEE, 2020.
% \end{itemize}

% \section{Publications}

\subsection*{Peer-reviewed Publications \hspace{5.5in}}
\begin{itemize}
    \item \underline{Chathuri Jayaweera}, Bonnie J. Dorr. \href{https://aclanthology.org/2025.nlperspectives-1.4/}{From Disagreement to Understanding: The Case for Ambiguity Detection in NLI}. In Proceedings of the 4th Workshop on Perspectivist Approaches to NLP (NLPerspectives), EMNLP 2025
    \item \underline{Chathuri Jayaweera}, Sangpil Youm, and Bonnie J. Dorr. \href{https://aclanthology.org/2024.fever-1.26/}{AMREx: AMR for Explainable Fact Verification}. In Proceedings of the 7th Fact Extraction and VERification Workshop (FEVER), EMLNP 2024
    % , pages 234–244, Association for Computational Linguistics, 2024
    \item Sangpil Youm, Brodie Mather, \underline{Chathuri Jayaweera}, Juliana Prada and Bonnie J. Dorr. \href{https://link.springer.com/chapter/10.1007/978-3-031-70239-6_29}{DAHRS: Divergence-Aware Hallucination Remediated SRL Projection}. In International Conference on Applications of Natural Language to Information Systems, Springer, 2024.
    \item Manuel Nunez Martinez, Sonja Schmer-Galunder, Zoey Liu, Sangpil Youm, \underline{Chathuri Jayaweera}, and Bonnie J. Dorr. \href{https://aclanthology.org/2024.sicon-1.7/}{Balancing Transparency and Accuracy: A Comparative Analysis of Rule-Based and Deep Learning Models in Political Bias Classification}. In Proceedings of the 2nd Workshop on Social Influence in Conversations (SICon 2024), EMNLP 2024.
    \item \underline{Chathuri Jayaweera} and Gihan Dias. \href{http://repo.sltc.ac.lk/handle/456/131}{Automatic Classification, Visualization and Analysis of Errors in Machine Translation}. In Extended Abstracts of International Conference on Information and Automation for Sustainability (ICIAFS), IEEE, 2021.
    \item Sutharsan, Mahendren, Shehan Rajakaruna, S. Y. Jayaweera, \underline{Chathuri Jayaweera}, and Subramaniam Thayaparan. \href{https://ieeexplore.ieee.org/abstract/document/9310872}{Vision-Based Adaptive Traffic Light Controller for Single Intersection}.In proceedings of the International Conference on Information Technology Research (ICITR), IEEE, 2020.
\end{itemize}
\vspace{-0.3in}
\subsection*{Manuscripts Under Review \hspace{5.5in}}
\begin{itemize}
    \item \underline{Chathuri Jayaweera}, Brianna Yanqui, Bonnie J. Dorr. \href{https://arxiv.org/abs/2507.15100}{Filling the Gap: Is Commonsense Knowledge Generation useful for Natural Language Inference?}. Annual Meeting of the Association for Computational Linguistics (ACL). Under-review. arXiv: 2507.15100, 2026
\end{itemize}
\vspace{-0.3in}
\subsection*{Preprints}
\begin{itemize}
    \item \underline{Chathuri Jayaweera} and Bonnie J. Dorr. \href{https://doi.org/10.5281/zenodo.18490000}{BLADE: Better Language Answers through Dialogue and Explanations}. Preprint 2026
\end{itemize}
